Comparing vector-based and ACT-R memory models using large-scale datasets:\protect\\User-customized hashtag and tag prediction on Twitter and StackOverflow

### 2014-11-24 writeups/dissertation/dissertation.tex
foo

>>>>

\subsubsection{Model Accuracy Differences Across Sites}

Model accuracy for StackOverflow was much higher overall than for Twitter.
The Twitter popular-hashtags dataset contained 400 unique hashtags for each of the four dataset subsets.
The StackOverflow randomly-sampled dataset contained \num{34377} unique tags, since it sampled posts across the entire site.
As the model is tasked to predict fewer and fewer hashtags, it should become more accurate (less chance of making an incorrect prediction).
However, even with a much smaller tag set to predict, model accuracy for Twitter was still not nearly as high as StackOverflow.
This is likely due to the fact that tag frequency use drops off sharply for both StackOverflow and Twitter.
This means that the models on both sites are generally switching between the top few hundred tags when making predictions.
So, increasing the total unique number of tags past that point makes only a small negative impact on model accuracy.

However, there was a large difference in total number of users for StackOverflow and Twitter.
A user on StackOverflow contributed 2.5 times more posts to the StackOverflow randomly-sampled dataset than the Twitter popular-hashtags dataset.
Also note that the large co-occurrence matrices for StackOverflow and Twitter that contained millions of documents were not user specific.
This means that the co-occurrence matrix for Twitter was built from a much larger set of unique users compared to StackOverflow.
It is likely that co-occurrence matrices for individual users are correlated but not equivalent.
So, as the co-occurrence matrix is built from a larger number of unique users, a greater amount of cross-user noise is introduced into the matrix.
This noise would decrease model accuracy since the contextual component of the model would lose predictive information by having a noisier co-occurrence matrix.
This is most likely one of the main reasons that model accuracy for Twitter is much lower than StackOverflow:
Tag prediction becomes much more challenging as the number of users on a site increases.

The second most-likely reason that model accuracy is much higher for StackOverflow is that the co-occurrence matrix for this site contains much more data due to the large document size for the site.
The co-occurrence matrix for the StackOverflow randomly-sampled dataset contained 20 times more observations than the matrix for one of the Twitter popular-hashtags datasets.
Model accuracy generally increases as more observations are used to generate the co-occurrence matrices, since this allows each cell in the matrix to stabilize to its true value.
